Titulo

### 2014-11-15 RotacionOutFlows/Paper/ms.tex
larger images correct
Rotation Model

%Document Class
\documentclass{latex/emulateapj}

%Packages and Commands
\include{latex/packages_commands}

@@

\section{Theoretical Background}
\label{sec:theo}
In this section we are going to describe the two different models that are used in this project, that are able to reproduce a real and consistent \lya profile.\\

@@

\subsection{Rotation Model}
---------------------------------------------------------------------\\
MISSING: \\
- Full explanation.\\
- Ref: Jaime And Juan Nicolas\\
-----------------------------------------------------------------------\\

@@

\bibliographystyle{latex/mn2e}
\bibliography{references}

>>>>

%Document Class
\documentclass{latex/emulateapj}
\usepackage{multirow,color,wrapfig,ulem}

%Packages and Commands
\include{latex/packages_commands}
\usepackage{multirow,color,wrapfig,ulem}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage[dvips]{epsfig}
\newcommand{\avg}[1]{\langle{#1}\rangle}
\newcommand{\nscatt}{\langle N_{\rm  scatt}\rangle}
\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha~}\else{Ly$\alpha$~}\fi}}
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}}
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm{M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}
\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm{M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}
\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}
\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}
%\newcommand{\lya}{{Lyman $\alpha$~}}
\newcommand{\clara}{{\texttt{CLARA}}~}
\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}
\newcommand{\hs}{{\hspace{1mm}}}
%\newcommand{\kms}{{\ifmmode{{\mathrm{\,km\ s}^{-1}}}\else{\,km~s$^{-1}$}\fi}}

@@

\section{Theoretical Background}
\label{sec:theo}
In this section we describe the two different models that are used in this project,
that are able to reproduce a real and consistent \lya profile. As first we implement
the rotation followed by an outflow.\\

@@

\subsection{Rotation Model}

We use the simplified rotation model developed by [garavito-camargo et al]
in which a rotating galaxy is modeled as a solid rotating sphere, with a homogeneous mixture
of hydrogen and dust. Photons can be initially at the center or can be
homogeneously distributed inside the sphere. The equations governing this
 solid-body rotation sphere in which the axys of rotation is defined to be allign
 with the $z$-axys are:

\begin{equation}
    v_{x}=-\frac{y}{R}V_{\rm max}, \label{subeq1}
\end{equation}
\begin{equation}
    v_{y}=\frac{x}{R}V_{\rm max}, \label{subeq2}
\end{equation}
\begin{equation}
    v_{z}=0, \label{subeq3}
\end{equation}
%

Where $R$ is the radius of the sphere and $V_{\rm max}$ is the linear
velocity at the sphere's surface. The minus/plus sign in the
$x$/$y$-component of the velocity indicates the direction of
rotation. In this case we take the angular velocity in the same
direction as the $\hat{k}$ unit vector.

In this work we use the analytical expression for rotation derived in [garavito-camargo et al]
where a rotating sphere can be seen as a static sphere in the laboratory
frame with a bulk velocity difference in each surface element with respect
to a distant observer. With the previous analysis the outcoming spectra can be
expressed as:

\begin{equation}
J(x,i) \approx 2\pi \int_0^Rdb \hs b
\int_0^{2\pi}d\phi \hs J(x,b,\phi,i),
\end{equation}

Where $J(x, b, \phi, i)$ is the spectrum of the flux emerging from the
surface at point $(b, \phi)$ and is expressed as:

\begin{equation}
J(x,b,\phi,i)=\frac{\sqrt{\pi}}{\sqrt{24}a\tau_0}\Bigg{(}\frac{(x-x_{\rm
    b})^2}{1+{\rm cosh}\Big{[}\sqrt{\frac{2\pi^3}{27}}\frac{|(x
      -x_{\rm b})^3|}{a\tau_0}\Big{]}}\Bigg{)}.
\end{equation}

@@

\bibliographystyle{apj}
\bibliography{references}
